---
title       : "Course 9 - Week 4 Project slides"
subtitle    : "11/7/2018"
author      : "Robert Deprizio"
job         : 
framework   : io2012 #{io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [shiny]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
https://github.com/ramnathv/slidify/issues/445

## Introduction

This app was designed to calculate the probability that a person taking a multiple choice test could pass strictly by randomly guessing. 

The calculation that runs in the backgrouund, which uses the binomial distribution, is based on parameters that the user specifies by the 3 slider inputs and is then passed to server code script. Further details can be found in the readMe file on my git hub link below if needed:



--- .class #id 

## Parameters

The parameters used in the calculation are inputted by the user when they specify the following 3 slider values:

- Number of multiple choice questions on the test 
- Number of choices for each question 
- Passing score/percentage required 

---

## R code: Front End of App
The below code allows the user to select the inputs that will be used to calculate the probability for the binomial distribution
```{r,echo=FALSE}
library(shiny)
library(shinyjs)
library(devtools)
# Define UI for application that calculates a probability

      sliderInput("questions",
                   "Number of questions:",
                   min = 1,
                   max = 50,
                   value = 1)
```

--- 

<style>
em {
  font-style: italic
}
</style>
```{r,echo=FALSE}
library(shiny)

# Define UI for application that calculates a probability

      sliderInput("questions",
                   "Number of questions:",
                   min = 1,
                   max = 50,
                   value = 1)
```
