---
title: "Course 9 - Week 3 project"
author: "Robert Deprizio"
date: "11/3/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

## R Markdown

In this presentation we'll examine a few of the basic features of the **Plotly** package using the **mtcars** data set that's prepackaged with R. For additional information on the package you'll want to visit

https://plot.ly/r/


## Downloading the Plotly package 

To download and install the **Plotly** package call the **install.packages("plotly")** function if you haven't already done so.  

## Plot 1 - R code
Using the code below we'll create some box plots to show the displacement amounts for each car by cylinder type (4,6,8). Note that we'll have to convert the **cyl** variable to a factor variable

```{r, echo = TRUE,results="hide",warning=FALSE}
library(plotly)
mtcars$cyl<-as.factor(mtcars$cyl)
p<-plot_ly(mtcars,y=~disp,color = ~cyl,type="box")
p
```

## Plot 1 output

Here we see that if we hover over the plots we can view the quartile amounts of the **displacement** variable for each cylinder type
```{r,warning=FALSE}
p<-plot_ly(mtcars,y=~disp,color = ~cyl,type="box")
p
```

##Plot 2- R code
The code below computes the mean of the **mpg** variable for each of the factors for the **am** variable where "0" represents manual transmission cars and "1" to denote cars with automatic transmissions
```{r, echo = TRUE,results="hide",warning=FALSE}
mtcars$am<-as.factor(mtcars$am)
averages<-aggregate(mtcars$mpg,by=list(mtcars$am),mean)
averages$Group.1<-as.factor(averages$Group.1)
second_plot<-plot_ly(x=averages$Group.1,y=averages$x,
                     color=averages$Group.1,type="bar")
second_plot
```

##Plot 2 - MPG averages by transmission 
If we hover the cursor over the bar representing automatic transmissions we can see that those cars have roughly an avg. mpg = 24 
```{r, echo = FALSE,warning=FALSE,fig.width=5, fig.height=7}
mtcars$am<-as.factor(mtcars$am)
averages<-aggregate(mtcars$mpg,by=list(mtcars$am),mean)
averages$Group.1<-as.factor(averages$Group.1)
second_plot<-plot_ly(x=averages$Group.1,y=averages$x,color = averages$Group.1,type="bar")
second_plot
```