---
title: "Course 9 - Week 4 Project slides"
author: "Robert Deprizio"
date: "11/11/2018"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

## Introduction

This app was designed to calculate the probability that a person taking a multiple choice test could pass strictly by randomly guessing. 

The calculation that runs in the backgrouund, which uses the binomial distribution, is based on parameters that the user specifies by the 3 slider inputs and is then passed to server code script. Further details can be found in the readMe file on my git hub link below if needed:



--- .class #id 

## Parameters

The parameters used in the calculation are inputted by the user when they specify the following 3 slider values:

- Number of multiple choice questions on the test 
- Number of choices for each question 
- Passing score/percentage required 

---

## R code: Front End of App
The code below is a snippet of one of the sliders that allow the user to select the number of questions (i.e. trials) which will be used to calculate the probability for the binomial distribution. Note: for some reason the slider input does not display properly though Slidify. Please see the ***Server.R*** and ***UI.R*** files on my github page for the full code: https://github.com/BD20171998/Course-9  
```{r,echo=TRUE,warning=FALSE}
library(shiny)
      sliderInput("questions","Number of questions:",min = 1,max = 50,
                   value = 1)
```

--- 

```{r,echo=FALSE,warning=FALSE}
library(shiny)
# Define UI for application that calculates a probability
ui <-shinyUI(fluidPage(
  br(),
  # Application title
  titlePanel("Input Parameters"),
  
  # Sidebar with a slider input for test inputs 
  sidebarLayout(
    sidebarPanel(
       fluidRow(
      
      sliderInput("questions",
                   "Number of questions:",
                   min = 1,
                   max = 50,
                   value = 1),
    
    sliderInput("choices",
                "Number of choices:",
                min = 2,
                max = 10,
                value = 2),
    
  sliderInput("passing_grade",
              "Passing grade needed:",
              min = 1,
              max = 100,
              value = 1),
  br(),
  
  #Button to return value
  actionButton("go","Calc.Prob."), 
  
  #Button to reset display and values
  actionButton("reset", "Clear")
)),
  
    # Show probability
    mainPanel(h3("What's the Probability You Can Pass a Multiple Choice Test Strictly by Guessing?"),
       br(),
       br(),
       h4(textOutput("disp",inline = TRUE),"%")
      
    )
  )
)
)
# Define server logic required to calculate the binomial probability
server<-shinyServer(function(input, output,session) {
  observeEvent(input$go, {
  output$disp <- renderText({
    
    # Calculate binomial probability and return as a percentage
    
   if(input$passing_grade==100)
   {x<-dbinom(input$questions,input$questions,1/input$choices)}
    
  else
    x    <- 1-pbinom(floor((input$passing_grade/100)*input$questions),input$questions,1/input$choices)
   
  x*100 
    
  })
  })
  
 #Reset slider values to default amounts
  observeEvent(input$reset,{
    updateSliderInput(session,"passing_grade",value=1)
    updateSliderInput(session,"questions",value = 1)
    updateSliderInput(session,"choices",value = 2)
    output$disp <- renderText({""})
    
  })
  
})
shinyApp(ui = ui, server = server)
```